\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-10-27 manuscript/ms_MicroMeso.Rnw
updated abstract

\begin{abstract}
The basic idea here is to do a head-to-head comparison of complex, individual-based integral projection models and less complex, ``patch-based" models. The problem is this: as ecologists we want to forecast the impacts of global change, like climate change, at scales relevant to land management decisions and policy intervention. However, almost all studies of plant population dynamics rely on data at the sub 1 meter scale. This data is really hard to collect. Can we use average plot cover to forecast plant population dynamics just as well as when we use complex IPMs? Can ``averaged-out" population models at the plot level adequately capture climate drivers? These are the questions we seek to answer here.
\end{abstract}

>>>>

\begin{abstract}
\noindent Forecasts of populations under future climate change are constrained by the spatial and temporal scales at which we can gather data. For plants, ecologists often require individual level data to build population models; data that is difficult and expensive to collect at spatial scales greater than one square meter. Models built using such data are difficult to scale-up to spatial scales relevant to land management decisions and policy intervention. A possible route forward are density-structured models based on coarse-scale census data, which are much easier to collect over large spatial extents. However, to use coarse-scale data in a climate change context requires the assumption that the climate signals in population dynamics identified using individual-level data can also be identified when individual-level data are averaged over. Here we use a longterm dataset to model population dynamics using individual-level and plot-level data.   
\end{abstract}
